Quantifying the coverage of ASVs within a species

### 2020-10-16 exploratory/2020-10-15-asv-species-coverage.Rmd
Add table showing counts of most abundant species, closes #30

---
title: "Quantifying the coverage of ASVs within a species"
author: "Pat Schloss"
date: "10/05/2020"
output:
  github_document:
    html_preview: false
editor_options: 
  chunk_output_type: console
---

```{r, message=FALSE}
library(tidyverse)
library(here)

@@

species_asvs <- metadata_asv %>% 
	select(genome_id, species, region, asv) %>%
	group_by(region, species) %>%
	summarize(n_genomes = n_distinct(genome_id),
						n_asvs = n_distinct(asv),
						asv_rate = n_asvs/n_genomes,
						.groups="drop")

@@

>>>>

---
title: "Quantifying the coverage of ASVs within a species"
author: "Pat Schloss"
date: "10/15/2020"
output:
  github_document:
    html_preview: false
editor_options: 
  chunk_output_type: console
---

```{r, message=FALSE}
library(tidyverse)
library(knitr)
library(here)

@@

species_asvs <- metadata_asv %>% 
	select(genome_id, species, region, asv, count) %>%
	group_by(region, species) %>%
	summarize(n_genomes = n_distinct(genome_id),
						n_asvs = n_distinct(asv),
						n_rrns = sum(count) / n_genomes,
						asv_rate = n_asvs/n_genomes,
						.groups="drop")

@@

```{r}
# species name, number of genomes, average number of rrns, number of ASVs across
# genomes for each region of 16S rRNA gene

count_table <- species_asvs %>%
	select(species, region, n_genomes, n_rrns, n_asvs) %>%	
	group_by(species) %>%
	mutate(n_genomes = max(n_genomes),
				 n_rrns = max(n_rrns)) %>%
	ungroup() %>% 
	pivot_wider(names_from=region, values_from=n_asvs) %>% 
	arrange(species)

#see also kableExtra
count_table %>%
	arrange(desc(n_genomes)) %>%
	top_n(n_genomes, n=10) %>%
	kable(caption = "Ten most commonly sequence species", digits=2)
```
